---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nreltools

<!-- badges: start -->
[![R-CMD-check](https://github.com/andypicke/nreltools/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andypicke/nreltools/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

[nreltools](https://github.com/andypicke/nreltools) provides functions for working with APIs and tools from the [NREL Developer Network](\https://developer.nrel.gov/) in R. 

To use the tools you will need to [sign up for a free API key](https://developer.nrel.gov/signup/). The package functions assume by defauls that you have stored your API Key as "NREL_DEVELOPER_API_KEY" in you .Renviron file.

## Installation

You can install the development version of nreltools like so:
```{r}
# install.packages("devtools")
devtools::install_github("andypicke/nreltools")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(nreltools)
## basic example code
```
